Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Conclusion fixes

	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is not a system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.

>>>>

	From this table, we come to the conclusion that there is no complete decentralized system that provides the full functionality and security that Tor offers today. While there is a lot of research on decentralized systems, there is no system yet that can compete with Tor. The systems that do exist such as Tarzan, Torsk and Gnutella are getting some things right, yet they often lack functionality such as anonymity, good routing performance or are vulnerable for a variety of attacks.
